`flippant` -- An `R` package for the automated  analysis of dithionite scramblase

### 2015-09-19 inst/manuscript/manuscript.rmd
Finishing a first draft of the "Main Features" section;

##Producing Protein To Phospholipid (PPR) Plots
```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
```

##Non-graphical Output of Analysis Results
```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
```

>>>>

##Scramblase Assay Analysis
Plotting protein to phospholipid ratio (PPR) against the likelyhood for a given
proteoliposome to contain one or more scramblases, the PPR plot is at the heart 
of the analysis of dithionite scramblase assays, allowing for the visual 
comparison of specific scramblase activity between interrogated experimental 
series, which may e.g. be representative of protein preparations including 
mutant protein forms or crude extracts with or without depletion of a candidate
scramblase. 
```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
```
allows for the complete generation of the PPR plot in publication quality from 
the user assembled spreadsheet of input data (`x`), including automatically 
added graphical representations of $\tau$, the PPR value equal to the fit 
constant $\alpha$, which implies all liposomes on average carrying one 
scramblase and 63% have one or more (i.e. are active). The behavior of the 
function may be adjusted to use scramblase-mediated fluorescense reduction 
normalized to either the maximum measurement in the series (`scaleTo = "data"`)
or the plateau of an exponential fit to it (`scaleTo = "model"`; for reasoning
see above) and whether or not to require the exponential curve fitted to the 
data to go through the origin.

Numeric scramblase assay results such as $\tau$ may be generated in tabular form
using
```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
```
with the same modifying arguments to the function as for `scramblaseAssayPlot`.
